Impact of Party Leadership on Donation Patterns

### 2024-12-04 paper/paper.qmd
Update idealized survey

**State of Residence:** Dropdown list of all provinces and
territories. - **Age:** Multiple-choice options (e.g., 18-24, 25-34,
etc.). - **Gender:** Options including Male, Female, Non-binary/Other,
Prefer not to say. - **Income Level:** Income brackets (e.g., Less than
\$25,000, \$25,000-\$49,999, etc.). - **Education Level:** Highest
degree obtained (e.g., High school, Bachelor’s, Master’s, etc.). -
**Occupation:** Open-ended or categorized options. - **Political
Affiliation:** Conservative, Liberal, NDP, Other.

**Section 2: Donation Behavior** - **Are you currently registered to
donate to political parties?** - Yes - No - **How frequently do you
donate to political parties?** - Never - Rarely (once a year or less) -
Occasionally (a few times a year) - Regularly (monthly or more) -
**Average Donation Amount:** Slider or multiple-choice options (e.g.,
Less than \$50, \$50-\$199, etc.). - **Preferred Donation Channels:**
Multiple selections (e.g., Online platforms, Mail-in donations,
In-person events, etc.).

**Section 3: Motivations for Donating** - **What motivates you to donate
to a political party?** (Select all that apply) - Support for specific
policies or issues - Desire to influence election outcomes - Loyalty to
the party or its leaders - Social pressure or community influence - Tax
benefits - Other (please specify) - **Which factors most influence your
decision to donate?** (Rank in order of importance) - Candidate's
leadership qualities - Party's stance on key issues - Party's past
performance - Recommendations from peers or influencers - Media
coverage - Other (please specify)

**Section 4: Impact of Campaigns and Events** - **Have recent political
events influenced your donation behavior?** - Yes - No - **If yes,
please specify the events and how they influenced your donations.**
(Open-ended) - **How do you perceive the effectiveness of political
campaigns in encouraging donations?** - Very ineffective - Ineffective -
Neutral - Effective - Very effective

**Section 5: Feedback and Suggestions** - **What could political parties
do to encourage more donations from supporters?** (Open-ended) - **Any
additional comments or suggestions regarding political donations?**
(Open-ended)

Survey Administration

1.  **Sampling Method:** Utilize stratified random sampling to ensure
    representation across different provinces, income levels, education
    backgrounds, and political affiliations. Oversample underrepresented
    groups to enhance data diversity.

2.  **Data Collection Modes:**

    -   **Online Surveys:** Distribute the survey through email
        invitations, social media platforms, and online panels to reach
        a broad audience.
    -   **Telephone Surveys:** Conduct phone interviews to include
        respondents who may have limited internet access or prefer
        verbal communication.
    -   **In-Person Interviews:** Organize face-to-face interviews in
        selected regions to capture detailed qualitative data.

3.  **Incentives:** Offer incentives such as entry into a sweepstakes,
    gift cards, or charitable donations to encourage participation and
    improve response rates.

4.  **Survey Length and Design:**

    -   **Duration:** Design the survey to be completed within 10-15
        minutes to minimize respondent fatigue.
    -   **Clarity:** Use clear and concise language, avoiding technical
        jargon to ensure respondents understand each question.
    -   **Question Types:** Employ a mix of multiple-choice, Likert
        scales, and open-ended questions to capture both quantitative
        and qualitative data.

5.  **Data Quality Measures:**

    -   **Pilot Testing:** Conduct a pilot survey to identify and
        rectify any issues with question wording, survey flow, or
        technical glitches.
    -   **Anonymity and Confidentiality:** Assure respondents that their
        answers are confidential and will be used solely for research
        purposes to encourage honest and accurate responses.
    -   **Response Validation:** Implement checks to prevent duplicate
        responses, ensure logical consistency, and verify the
        completeness of the survey.

6.  **Data Analysis:**

    -   **Weighting:** Apply weighting adjustments to account for any
        sampling biases and ensure that the survey results accurately
        reflect the population demographics.
    -   **Statistical Techniques:** Use appropriate statistical methods
        to analyze the data, identifying significant predictors of
        donation behavior and uncovering underlying trends.

>>>>

**State of Residence:** - Dropdown list of all provinces and
territories.

**Age:** Multiple-choice options

-   18-24

-   25-34

-   35-44

-   45-54

-   55-64

**Gender:**

-   Male

-   Female

-   Non-binary/Other

-   Prefer not to say.

**Income Level:**

-   Less than \$25,000

-   \$25,000-\$49,999

-   \$50,000 - \$74,999

-   \$75,000 - \$99,000

-   \$100,000 - \$149,000

-   \$150,000 or more

**Education Level:** Highest degree obtained

-   Less than high school

-   High school diploma or equivalent

-   Some college, no degree

-   Associate degree

-   Bachelor's degree

-   Graduate or professional degree

**Political Affiliation:**

-   Conservative

-   Liberal

-   NDP

-   Other (please specify)

**Section 2: Donation Behavior**

**Are you currently registered to donate to political parties?**

-   Yes

-   No

**How frequently do you donate to political parties?**

-   Never

-   Rarely (once a year or less)

-   Occasionally (a few times a year)

-   Regularly (monthly or more)

**Average Donation Amount:**

-   Less than \$200

-   \$200 - \$1,000

-   \$1,001 - \$5,000

-   \$5,001 - \$10,000

-   More than \$10,000

**Preferred Donation Channels:**

-   Online platforms

-   Mail-in donations

-   In-person events

**Section 3: Motivations for Donating**

**What motivates you to donate to a political party?** (Select all that
apply)

-   Support for specific policies or issues

-   Desire to influence election outcomes

-   Loyalty to the party or its leaders

-   Social pressure or community influence

-   Tax benefits

-   Other (please specify)

**Which factors most influence your decision to donate?** (Select all
that apply)

-   Candidate's leadership qualities

-   Party's stance on key issues

-   Party's past performance

-   Recommendations from peers or influencers

-   Media coverage

-   Other (please specify)

**Section 4: Impact of Campaigns and Events**

**Have recent political events influenced your donation behavior?**

-   Yes

-   No

**If yes, please specify the events and how they influenced your
donations.** (Open-ended)

**How do you perceive the effectiveness of political campaigns in
encouraging donations?**

-   Very ineffective

-   Ineffective

-   Neutral

-   Effective

-   Very effective

**Section 5: Feedback and Suggestions**

**What could political parties do to encourage more donations from
supporters?** (Open-ended) -

**Any additional comments or suggestions regarding political
donations?** (Open-ended)
